Hidden Talents Multiverse Analysis

### 2021-02-08 README.Rmd
separate script input-output table in README

Each script takes an input(s) and produces output(s). The table below provides an overview of the inputs and outputs of each script.

@@

    tibble(
      dir       = x %>% str_remove_all("scripts/") %>% str_remove_all("/.*") %>% str_remove("^\\d-"),
      script    = x %>% str_remove_all(".*/"),
      raw       = script_text %>% str_squish() %>% str_c(collapse = ", "),
      n_input   = str_count(script_text[1], "input"),
      input1    = script_text[1],
      input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br>") %>% ifelse(is.na(.),"",.),
      n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
      output1   = script_text[2],
      output2   = output1 %>% str_remove_all("output: ") %>% str_trim(),
      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "\n- ") %>%  paste0("- ", .) %>% ifelse(. == "- NA","",.)
    )
  })

file_list %>% 
  select(dir,script, input, output) %>% 
  gt(id = "one", rowname_col = "row", groupname_col = "dir") %>% 
  fmt_markdown(columns = T) %>% 
  gt::as_raw_html()
```

>>>>

Each script takes an input(s) and produces output(s). The tables below provides an overview of the inputs and outputs of each script.

@@

    tibble(
      dir       = x %>% str_remove_all("scripts/") %>% str_remove_all("/.*") %>% str_remove("^\\d-"),
      script    = x %>% str_remove_all(".*/"),
      raw       = script_text %>% str_squish() %>% str_c(collapse = ", "),
      n_input   = str_count(script_text[1], "input"),
      input1    = script_text[1],
      input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>%str_c(collapse = "\n- ") %>%  paste0("- ", .) %>% ifelse(. == "- ","",.),
      n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
      output1   = script_text[2],
      output2   = output1 %>% str_remove_all("output: ") %>% str_trim(),
      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "\n- ") %>%  paste0("- ", .) %>% ifelse(. == "- NA","",.)
    )
  }) 
```

### Data Prep

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "data-prep") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = T) %>% 
  as_raw_html()
```

### Primary Analyses

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "primary-analyses") %>% 
  select(-dir) %>% 
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = T) %>% 
  as_raw_html()
```

### Seconary Analyses

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "secondary-analyses") %>% 
  select(-dir) %>% 
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = T) %>% 
  as_raw_html()
```
